Making Sequential Programs Deterministic

### 2019-03-25 design.tex
type validity rules
fewer examples

\todo{It is very important to express the whole section as formal type
  jugdments, or we will get laughed
  out of the room as amateurs, during the program committee meeting.  Also,
  the formalism will help make the ideas precise.

  Type well-formedness rules:\todo{format nicely in \LaTeX}

  antecedent: $\Gamma : \kappa_e <: \kappa_c$

  consequent: $\Gamma : \kappa_c \ \codeid{List}\langle\kappa_e\ 
  \codeid{Object}\rangle$
  }

@@

\todo{Fewer examples, less variation.  Use \<List> and \<String>.}

Some examples of valid types are:
\begin{itemize}
    \item \codeid{@NonDet\ \ \ \ \ \ List<@NonDet\ \ \ \ \ \ Integer>}
    \item \codeid{@Det\ \ \ \ \ \ \ \ \ List<@Det\ \ \ \ \ \ \ \ \ Integer>}
    \item \codeid{@OrderNonDet Set <@OrderNonDet Set<...>\relax >}
    \item \codeid{@OrderNonDet Set <@Det String>}
    \item \codeid{@Det\ \ \ \ \ \ \ \ \ Map <@Det String, @Det Integer>}
    \item \codeid{@NonDet\ \ \ \ \ \ Set <T extends @NonDet Object>}
\end{itemize}

These types are invalid:
\begin{itemize}
    \item \codeid{@OrderNonDet Set <@NonDet\ \ \ \ \ \ Integer>}
    \item \codeid{@NonDet\ \ \ \ \ \ List<@Det\ \ \ \ \ \ \ \ \ Integer>}
    \item \codeid{@NonDet\ \ \ \ \ \ List<@OrderNonDet Set<...>\relax >}
    \item \codeid{@Det\ \ \ \ \ \ \ \ \ List<@NonDet\ \ \ \ \ \ Integer>}
    \item \codeid{@Det\ \ \ \ \ \ \ \ \ List<@OrderNonDet Set<...>\relax >}
    \item \codeid{@Det\ \ \ \ \ \ \ \ \ Map <@Det String, @OrderNonDet List<@Det String>>}
    \item \codeid{@Det\ \ \ \ \ \ \ \ \ List<T extends @NonDet Object>}
    \item \codeid{@NonDet\ \ \ \ \ \ Set\ <T extends @Det Object>}
\end{itemize}

@@

For example, these types are valid:
\begin{itemize}
    \item \codeid{@NonDet int @NonDet \ \ \ \ []}
    \item \codeid{@Det \ \ \ int @Det \ \ \ \ \ \ \ []}
    \item \codeid{@Det \ \ \ int @OrderNonDet[] @OrderNonDet[]}
\end{itemize}

These types are invalid:
\begin{itemize}
    \item \codeid{@NonDet int @OrderNonDet[]}
    \item \codeid{@NonDet int @Det \ \ \ \ \ \ \ []}
    \item \codeid{@Det \ \ \ int @NonDet \ \ \ \ []}
\end{itemize}

>>>>

%\todo{It is very important to express the whole section as formal type
%  jugdments, or we will get laughed
%  out of the room as amateurs, during the program committee meeting.  Also,
%  the formalism will help make the ideas precise.
%
%  Type well-formedness rules:\todo{format nicely in \LaTeX}
%
%  antecedent: $\Gamma : \kappa_e <: \kappa_c$
%
%  consequent: $\Gamma : \kappa_c \ \codeid{List}\langle\kappa_e\ 
%  \codeid{Object}\rangle$
%  }
Type validity rules:

$\infer[ANY TYPE]{\vdash : \kappa \  \tau}{\kappa : @Det / @NonDet}$

%$\infer[COLLECTION TYPE]{\vdash : \kappa \  \tau}{\kappa : @OrderNonDet & \tau : Collection/Map/Iterator/array}$

$\infer[ORDERNONDET \ COLLECTION]{\vdash : \kappa_c <\kappa_e \ \tau_e> \tau_c}{\kappa_c : @OrderNonDet/@Det & \kappa_e <: \kappa_c & \tau_c <: Collection/Map/Iterator}$

$\infer[ORDERNONDET \ ARRAY]{\vdash : \kappa_c [\kappa_e \ \tau_e] \tau_c}{\kappa_c : @OrderNonDet/@Det & \kappa_e <: \kappa_c }$

$\infer[NONDET \ COLLECTION]{\vdash : \kappa_c <\kappa_e \ \tau_e> \tau_c}{\kappa_c : @NonDet & \kappa_e : @NonDet & \tau_c <: Collection/Map/Iterator}$

$\infer[NONDET \ ARRAY]{\vdash : \kappa_c [\kappa_e \ \tau_e] \tau_c}{\kappa_c : @NonDet & \kappa_e : @NonDet }$

@@

%\todo{Fewer examples, less variation.  Use \<List> and \<String>.}

Some examples of valid types are:
\begin{itemize}
    \item \codeid{@NonDet\ \ \ \ \ \ List<@NonDet\ \ \ \ \ \ Integer>}
    \item \codeid{@Det\ \ \ \ \ \ \ \ \ List<@Det\ \ \ \ \ \ \ \ \ Integer>}
    \item \codeid{@OrderNonDet List <@OrderNonDet Set<...>\relax >}
    \item \codeid{@OrderNonDet List <@Det String>}
\end{itemize}

These types are invalid:
\begin{itemize}
    \item \codeid{@OrderNonDet Set <@NonDet\ \ \ \ \ \ Integer>}
    \item \codeid{@NonDet\ \ \ \ \ \ List<@Det\ \ \ \ \ \ \ \ \ Integer>}
    \item \codeid{@Det\ \ \ \ \ \ \ \ \ List<@OrderNonDet Set<...>\relax >}
\end{itemize}

@@
